Verifying Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
changed title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
updated abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\documentclass[10pt,conference]{IEEEtran}
% \documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\bibliographystyle{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{textcomp}
\usepackage{xcolor}
\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
Software verification has experienced significant progress over the last two decades. Currently, there exist various software verifies that are able to solve intricate real-world problems, e.g., to design and verify renewable and stand-alone solar photovoltaic (PV) systems. 
Currently around $1$ billion of people do not have electrical energy; energy poverty alleviation has become an important political issue. 
%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
Particular attention is given to renewables and PV systems. Unfortunately, existing tools available to evaluate PV designs are mainly based on simulations that do not cover all aspects of the design space. 
The use of automated verification in PV systems is a recent subject with only a few initiatives. 
Here we develop an optimization algorithm and report its preliminary results using three state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing. 
Our proposal is unprecedented and interesting to streamline the design and analysis of PV systems. Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
\end{abstract}

>>>>

\documentclass[10pt,conference]{IEEEtran}
% \documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\bibliographystyle{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{textcomp}
\usepackage{xcolor}
\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

 \renewcommand{\baselinestretch}{0.97}

\begin{document}

\title{Verifying Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
Software verification has experienced significant progress over the last two decades. 
Currently, there exist various software verifies that are able to formally check real-world 
applications from energy systems, telecommunications, digital control and medical devices.
Our main focus here is on renewable and stand-alone solar photovoltaic (PV) systems. 
Currently we have approximately $1$ billion of people who do not have electrical energy; 
energy poverty alleviation has become an important political issue. 
%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
Particular attention is given to renewables and PV systems. 
Unfortunately, state-of-the-art tools available to evaluate PV designs are mainly based on simulations, 
which do not cover all aspects of the design-space. 
The application of automated verification to PV systems is a very recent subject with only a few initiatives. 
Here we develop an optimization algorithm and report preliminary results using three state-of-art software 
verifiers with the goal of optimizing the sizing of a PV system. Commercial equipment data is part of our specification 
and the technical solution is derived from financial analysis of the obtained sizing. Our proposal is novel and 
unprecedented to streamline the design and analysis of PV systems. 
Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
\end{abstract}
